---
title: "Modifications of corneal cross-linking protocols- pepsin assay"
author: "Malwina Kowlaska"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: TRUE
    toc_float: true
---

```{r setup, include=FALSE}
library("tidyverse")
library("RColorBrewer")
library("DescTools")
library("multcomp")
library("lmtest")
library(readxl)
library(dplyr)
library(ggplot2)
```

```{r, include=FALSE}
#directory
setwd("C:/Users/yoga/OneDrive - Universit채t Z체rich UZH/backup/Work/Lab_UZH/PepsinDigestion/New")

Dat<-read_excel("DataAll.xlsx")
CCT<-read_excel("DataCCT.xlsx")
```


```{r, include=FALSE}
## CCT data in=mputation ##
which(CCT$mm == 7)

CCT[241,4] <- NA
CCT[242,4] <- NA
CCT[243,4] <- NA
CCT[244,4] <- NA
CCT[245,4] <- NA
CCT[246,4] <- NA
CCT[247,4] <- NA
CCT[248,4] <- NA
CCT[249,4] <- NA
CCT[250,4] <- NA
CCT[251,4] <- NA
CCT[252,4] <- NA
CCT[253,4] <- NA
CCT[254,4] <- NA
CCT[255,4] <- NA
CCT[256,4] <- NA
CCT[257,4] <- NA
CCT[258,4] <- NA
CCT[259,4] <- NA
CCT[260,4] <- NA

CCT[764,4] <- NA
CCT[765,4] <- NA
CCT[766,4] <- NA
CCT[767,4] <- NA
CCT[768,4] <- NA
CCT[769,4] <- NA
CCT[770,4] <- NA
CCT[771,4] <- NA
CCT[772,4] <- NA
CCT[773,4] <- NA
CCT[774,4] <- NA
CCT[775,4] <- NA
CCT[776,4] <- NA
CCT[777,4] <- NA
CCT[778,4] <- NA
CCT[779,4] <- NA
CCT[780,4] <- NA
CCT[781,4] <- NA
CCT[782,4] <- NA
CCT[783,4] <- NA

CCT[794,4] <- NA
CCT[901,4] <- NA
```

```{r, echo= FALSE, include=FALSE}
library(missForest)

CCT$Tx<- as.factor(CCT$Tx)
CCT$CCT<- as.factor(CCT$CCT)

apply(CCT,2,function(x) sum(is.na(x)))
CCT.r <- CCT[,c(3:5,8,10)]

dim(CCT.r)
str(CCT.r)

CCT.r <- as.data.frame(CCT.r)

set.seed(12345689)
CCT.imp <- missForest(CCT.r, verbose = TRUE, variablewise = TRUE) 
CCT.imp$OOBrerror

CCT.i <- CCT.imp$ximp

CCT.i$mm[241]
CCT.i$mm[783]

apply(CCT.i,2,function(x) sum(is.na(x)))

CCT.i$DW <- CCT$DW
CCT.i$Ex <-CCT$Ex
CCT.i$DW<-as.factor(CCT.i$DW)
str(CCT.i)
```

```{r, echo=FALSE, include=FALSE}
CCTA<- CCT.i %>%
  filter(Ex=="Acc") %>%
  ggplot(aes(x= Tx, y= mm, color=CCT))+
  geom_boxplot()+
  theme_bw()+
  ylim(500,1000)+ #yaxixs limits
  theme(legend.position = "right")+
  theme(text = element_text(color = "black"),
        plot.subtitle=element_text(size=12),
        axis.title= element_text(size=10),
        axis.text.x = element_text(size = 10, colour = "black"),
        axis.text.y = element_text(size = 10), 
        strip.background = element_rect(fill="grey"),
        strip.text = element_text(size = 10),
        axis.title.x = element_blank(), # remove x axis title
        panel.grid.major.x = element_blank(),# remove vertical lines
        panel.grid.minor = element_blank(), #remove part of a grid
        legend.position = "none" 
        )+
  labs(title="Acceleration", 
       y=expression("Thicknes"~(mu*m)), x="Treatment group") +
  scale_color_manual(values=c("#dfc27d", "#018571"))+ 
  scale_x_discrete (limits=c("0","300","1","20"),
                    labels=c("Control","30 min","10 min","2 min"))

CCTB<- CCT.i %>%
  filter(Ex=="B2") %>%
  ggplot(aes(x= Tx, y= mm, color=CCT))+
  geom_boxplot()+
  theme_minimal()+
  theme_bw() +
  ylim(500,1000)+
  theme(text = element_text( color = "black"),
        plot.subtitle=element_text(size=10),
        axis.title= element_text(size=10),
        axis.text.x = element_text(size = 10, colour = "black"),
        axis.text.y = element_text(size = 10), 
        strip.background = element_rect(fill="grey"),
        strip.text = element_text(size = 10),
        axis.title.x = element_blank(), 
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "none" #remove legend
        )+
  labs(title="Riboflavin concentration", 
       y=expression("Thicknes"~(mu*m)), x="Treatment group") +
  scale_color_manual(values=c("#dfc27d", "#018571"))+ 
  scale_x_discrete (labels = c('Control',expression(0.1 ~B[2]),expression(0.1 ~B[2]+~D[2]~O), expression(0.4 ~B[2]), expression(0.4 ~B[2]+~D[2]~O)))

CCTE<- CCT.i %>%
  filter(Ex %in% c('En1','En2')) %>%
  ggplot(aes(x= Tx, y= mm, color=CCT))+
  geom_boxplot()+
  theme_bw()+
  ylim(500,1000)+
  theme(text = element_text( color = "black"),
        plot.subtitle=element_text(size=12),
        axis.title= element_text(size=10),
        axis.text.x = element_text(size = 10, colour = "black"),
        axis.text.y = element_text(size = 10), 
        strip.background = element_rect(fill="grey"),
        strip.text = element_text(size = 10),
        axis.title.x = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "none" #remove legend
        )+
  labs(title="Fluence",
       y=expression("Thicknes"~(mu*m)), x="Treatment group") +
  scale_color_manual(values=c("#dfc27d", "#018571"))+ 
  scale_x_discrete (limits=c("0","1","2","3","4","5","6"), 
                    labels = c('Control','5.4'~J/cm^2,'10.8'~J/cm^2, '16.2'~J/cm^2, '21.6'~J/cm^2,'27'~J/cm^2, '32.4'~J/cm^2 ))

CCTH<- CCT.i %>%
  filter(Ex== "D_M") %>%
  ggplot(aes(x= Tx, y= mm, color=CCT))+
  geom_boxplot()+
  theme_bw()+
  ylim(500,1000)+
  theme(text = element_text(color = "black"),
        plot.subtitle=element_text(size=12),
        axis.title= element_text(size=10),
        axis.text.x = element_text(size = 10, colour = "black"),
        axis.text.y = element_text(size = 10), 
        strip.background = element_rect(fill="grey"),
        strip.text = element_text(size = 10),
        panel.grid.major.x = element_blank(), 
        panel.grid.minor = element_blank(),
        legend.position = "right",
        legend.key.size = unit(1.5, "cm"), #change legend size
        legend.key.width = unit(1,"cm")
        )+
  labs(title="Carrier agent", 
       y=expression("Thicknes"~(mu*m)), x="Treatment group") +
  scale_color_manual(values=c("#dfc27d", "#018571"))+ 
  scale_x_discrete (labels = c('Control','Dextran', 'HPMS'))

CCTR<- CCT.i %>%
  filter(Ex== "Rep") %>%
  ggplot(aes(x= Tx, y= mm, color=CCT))+
  geom_boxplot()+
  theme_bw()+
  ylim(500,1000)+
  theme(text = element_text(color = "black"),
        plot.subtitle=element_text(size=12),
        axis.title= element_text(size=10),
        axis.text.x = element_text(size = 10, colour = "black"),
        axis.text.y = element_text(size = 10), 
        strip.background = element_rect(fill="grey"),
        strip.text = element_text(size = 10),
        panel.grid.major.x = element_blank(), 
        panel.grid.minor = element_blank(),
        legend.position = "right",
        legend.key.size = unit(1.5, "cm"), #change legend size
        legend.key.width = unit(1,"cm")
        )+
  labs(title="Replacemnet", 
       y=expression("Thicknes"~(mu*m)), x="Treatment group") +
  scale_color_manual(values=c("#dfc27d", "#018571"))+ 
  scale_x_discrete (limits=c("0","yes_r","no_r"),
                    labels = c('Control','YES','NO'))
```

#CCT

##Graphs
```{r, echo=FALSE}
library("cowplot")

plot_grid(CCTA, CCTB, CCTE, CCTH,CCTR,
          labels = c("A", "B", "C", "D", "e"),
          ncol = 1, nrow = 4)
```

##Summary 

CCTA before saturation with riboflavin
CCTB after saturation with riboflavin
```{r, include=FALSE}
CCT.i$Group<-as.factor(CCT.i$Group)

CorneaA <- CCT.i %>%
  filter(CCT == "CCTA")

CorneaB <- CCT.i %>%
  filter(CCT == "CCTB")
```

```{r, echo=FALSE}
CorneaA %>%
  group_by(Ex, Tx) %>%
  summarise(SD = sd(mm), Mean= mean(mm), Min= min(mm), Max=max(mm))
```
```{r, echo=FALSE}
CorneaB %>%
  group_by(Ex, Tx) %>%
  summarise(SD = sd(mm), Mean= mean(mm), Min= min(mm), Max=max(mm))
```

#Acceleration

- 0- control
- 2- 2min, total delivered energy 5.4 J/cm2
- 10- 10 min, total delivered energy 5.4 J/cm2
- 30- 30min, total delivered energy 5.4 J/cm2

```{r, include=FALSE}
Dat[c(3,7:9,11)] <- lapply(Dat[c(3,7:9,11)], factor)

Acc <- Dat %>%
  filter(Ex == "Acc")

str(Acc)
summary(Acc)

Day8 <- subset(Acc, DW == 8)
Day16 <- subset(Acc, DW== 16)
```

*Is there a difference in CCTB between treatment groups*
```{r, echo=FALSE}
TukeyHSD(aov(data = Day8, CCTB~Tx))
TukeyHSD(aov(data = Day16, CCTB~Tx))
```

###Weight
- Weight of samples day 8
```{r, echo=FALSE}
Day8 %>%
  group_by(Tx) %>%
  summarize(Mean=mean(Sample),sdSample=sd(Sample), Minimum=min(Sample), Maximum=max(Sample), count = n())
```

- Weight of samples day 16
```{r, echo=FALSE}
Day16 %>%
  group_by(Tx) %>%
  summarize(Mean=mean(Sample),sdSample=sd(Sample), Minimum=min(Sample), Maximum=max(Sample), count = n())
```

###Modeling
- **Model day 8 WEIGHT**
```{r,}
mod1<-lm(Sample ~ Tx + CCTB + Group, data=Day8)
summary(mod1)
```

- Confidence intervals
```{r, echo=FALSE}
confint(mod1)
```

- Diferences between treatment groups
```{r, echo=FALSE}
mul <- glht(mod1, linfct = mcp(Tx = "Tukey")) # replace Tukey with Dunnett
summary(mul)
```

- **Model day 16 WEIGHT**
```{r}
mod2<-lm(Sample ~ Tx + CCTB + Group, data=Day16)
summary(mod2)
```

- Confidence Intervals
```{r, echo=FALSE}
confint(mod2)
```

- Difrences between treatment groups
```{r, echo=FALSE}
mul <- glht(mod2, linfct = mcp(Tx = "Tukey")) # replace Tukey with Dunnett
summary(mul)
```

###Models assumption check

- Day 8
```{r, echo=FALSE}
par(mfrow=c(2,2))
plot(mod1)
```

- Day 16
```{r, echo=FALSE}
par(mfrow=c(2,2))
plot(mod2)
```

###Plots
```{r, include=FALSE}
levels(Acc$DW)[levels(Acc$DW)=="8"] <- "Day 8"
levels(Acc$DW)[levels(Acc$DW)=="16"] <- "Day 16"
```

```{r, echo=FALSE}
Acc %>%
  ggplot(aes(x= factor(Tx, level = c("0","300","1", "20")) , y= Sample, group=Tx))+
  geom_boxplot(size=1) +
  theme_bw() +
  theme(text = element_text(color = "black"),
        plot.title=element_text(size=20, vjust = - 11, hjust = 0.07, face= "bold"),
        plot.subtitle=element_text(size=12),
        axis.title= element_text(size=16),
        axis.text.x = element_text(size = 16, face="bold", colour = "black"),
        axis.text.y = element_text(size = 16), 
        strip.background = element_rect(fill="grey"),
        strip.text = element_text(size = 18),
        axis.title.x = element_blank(), # remove x axis title
        panel.grid.major.x = element_blank() # remove vertical lines
        )+
  labs(title="Acceleration",
       x=expression("Treatment group"),
       y=expression("Weight"~(mu*g)))+
  scale_x_discrete (labels=c("Control","30 min","10 min","2 min")) + 
  facet_grid (DW~., scales="free_y")
```

#Fluence

Six energy modifications (treatment groups): 

- 0- control
- 1- 5.4 J/cm2
- 2- 10.8 J/cm2
- 3- 16.2 J/cm2
- 4- 21.6 J/cm2
- 5- 27 J/cm2
- 6- 32.4 J/cm2

Energy experiment was performed in two parts. 

- In the first part 5.4 J/cm2, 10.8 J/cm2, 16.2 J/cm2 
- In the second part 16.2 J/cm2, 21.6 J/cm2, 27 J/cm2, 32.4 J/cm2 

```{r, include=FALSE}
En<-Dat%>%
  filter(Ex %in% c('En1','En2'))

En8 <- subset(En, DW == 8)
En16 <- subset(En, DW== 16)
```

###Weight
- Weight of samples day 8
```{r, echo=FALSE}
En8 %>%
  group_by(Tx) %>%
  summarize(Mean=mean(Sample),SD=sd(Sample), Minimum=min(Sample), Maximum=max(Sample),count = n())
```

- Weight of samples day 16
```{r, echo=FALSE}
En16 %>%
  group_by(Tx) %>%
  summarize(Mean=mean(Sample),SD=sd(Sample), Minimum=min(Sample), Maximum=max(Sample),count = n())

```

###Model building

- **DAY8**
```{r, echo=FALSE}
mod8<-lm(Sample ~ Tx + CCTB + Group, data=En8)
summary(mod8)
```

- confident interval
```{r, echo=FALSE}
confint(mod8)
```

- group comparison
```{r, echo=FALSE}
mul <- glht(mod8, linfct = mcp(Tx = "Tukey")) # replace Tukey with Dunnett
summary(mul)
```

- **DAY 16**
```{r, echo=FALSE}
mod16<-lm(Sample ~ Tx + CCTB + Group, data=En16)
summary(mod16)
```

- Conf Intervals
```{r, echo=FALSE}
confint(mod16)
```

- group comparison
```{r, echo=FALSE}
mul <- glht(mod16, linfct = mcp(Tx = "Tukey")) # replace Tukey with Dunnett
summary(mul)
```

###Models assumption check

- Day 8
```{r, echo=FALSE}
par(mfrow=c(2,2))
plot(mod8)
```

- Day 16
```{r, echo=FALSE}
par(mfrow=c(2,2))
plot(mod16)
```

###Plots
```{r, echo=FALSE, include=FALSE}
levels(En$DW)[levels(En$DW)=="8"] <- "Day 8"
levels(En$DW)[levels(En$DW)=="16"] <- "Day 16"
```

```{r, echo=FALSE}
PlotE<-En %>%
  ggplot(aes(x= Tx, y= Sample, group=Tx))+
  geom_boxplot(size=1)+
  theme_bw() +
  theme(text = element_text(color = "black"),
        plot.title=element_text(size=20, vjust = - 11, hjust = 0.07, face= "bold"),
        plot.subtitle=element_text(size=12),
        axis.title= element_text(size=16),
        axis.text.x = element_text(size = 16, face="bold", colour = "black"),
        axis.text.y = element_text(size = 16), 
        strip.background = element_rect(fill="grey"),
        strip.text = element_text(size = 18),
         panel.grid.major.x = element_blank() # remove vertical lines
        )+
  labs(title="Fluence",
       x=expression("Treatment group"),
       y=expression("Weight"~(mu*g)))+
  scale_x_discrete(labels = c('Control','5.4'~J/cm^2,'10.8'~J/cm^2, '16.2'~J/cm^2, '21.6'~J/cm^2,'27'~J/cm^2, '32.4'~J/cm^2 ))+
  facet_grid (DW~., scales="free_y")

ggsave("PlotE.png", width = 22,
  height = 14,
  units = c( "cm"))

PlotE

```

# Riboflavin concentration and D20 supplementation

```{r, echo=FALSE, include=FALSE}
B2 <- Dat %>%
  filter(Ex == "B2")

Day8 <- subset(B2, DW == 8)
Day16 <- subset(B2, DW== 16)
```

###Weight
- Weight of samples day 8
```{r, echo=FALSE}
Day8 %>%
  group_by(Tx) %>%
  summarize(Mean=mean(Sample),sdSample=sd(Sample), Minimum=min(Sample), Maximum=max(Sample), count = n())
```

- Weight of samples day 16
```{r, echo=FALSE}
Day16 %>%
  group_by(Tx) %>%
  summarize(Mean=mean(Sample),sdSample=sd(Sample), Minimum=min(Sample), Maximum=max(Sample), count = n())
```

### Model

- **Model day 8 WEIGHT**
```{r,}
mod1<-lm(Sample ~ Tx + CCTB + Group, data=Day8)
summary(mod1)
```

- Confidence intervals
```{r, echo=FALSE}
confint(mod1)
```

- Diferences between treatment groups
```{r, echo=FALSE}
mul <- glht(mod1, linfct = mcp(Tx = "Tukey")) # replace Tukey with Dunnett
summary(mul)
```

- **Model day 16 WEIGHT**
```{r}
mod2<-lm(Sample ~ Tx + CCTB + Group, data=Day16)
summary(mod2)
```

- Confidence Intervals
```{r, echo=FALSE}
confint(mod2)
```

- Difrences between treatment groups
```{r, echo=FALSE}
mul <- glht(mod2, linfct = mcp(Tx = "Tukey")) # replace Tukey with Dunnett
summary(mul)
```

###Models assumption check

- Day 8
```{r, echo=FALSE}
par(mfrow=c(2,2))
plot(mod1)
```

- Day 16
```{r, echo=FALSE}
par(mfrow=c(2,2))
plot(mod2)
```

###Plots
```{r, include=FALSE}
levels(B2$DW)[levels(B2$DW)=="8"] <- "Day 8"
levels(B2$DW)[levels(B2$DW)=="16"] <- "Day 16"
```

```{r, echo=FALSE}
PlotB<- B2 %>%
  ggplot(aes(x= Tx, y= Sample, group=Tx))+
  geom_boxplot(size=1) +
  theme_bw() +
  theme(text = element_text( color = "black"),
        plot.title=element_text(size=20, vjust = - 11, hjust = 0.07, face= "bold"),
        plot.subtitle=element_text(size=12),
        axis.title= element_text(size=16),
        axis.text.x = element_text(size = 16, face="bold", colour = "black"),
        axis.text.y = element_text(size = 16), 
        strip.background = element_rect(fill="grey"),
        strip.text = element_text(size = 18),
        axis.title.x = element_blank(), # remove x axis title
        panel.grid.major.x = element_blank() # remove vertical lines
        )+
  labs(title="Rabioflavin concentration",
       x=expression("Treatment group"),
       y=expression("Weight"~(mu*g)))+
  scale_x_discrete(labels = c('Control',expression(0.1 ~B[2]),expression(0.1 ~B[2]+ ~D[2]~O), expression(0.4 ~B[2]), expression(0.4 ~B[2]+ ~D[2]~O)))+
  facet_grid (DW~., scales="free_y")

PlotB
```

#Riboflavin carrier

```{r, include=FALSE}
D_M <- Dat %>%
  filter(Ex == "D_M")

Day8 <- subset(D_M, DW == 8)
Day16 <- subset(D_M, DW== 16)
```

*Is there a difference in CCTB between treatment groups*

- day 16 only to control group
```{r, echo=FALSE}
TukeyHSD(aov(data = Day8, CCTB~Tx))
TukeyHSD(aov(data = Day16, CCTB~Tx))
```

###Weight
- Weight of samples day 8
```{r, echo=FALSE}
Day8 %>%
  group_by(Tx) %>%
  summarize(Mean=mean(Sample),sdSample=sd(Sample), Minimum=min(Sample), Maximum=max(Sample), count = n())
```

- Weight of samples day 16
```{r, echo=FALSE}
Day16 %>%
  group_by(Tx) %>%
  summarize(Mean=mean(Sample),sdSample=sd(Sample), Minimum=min(Sample), Maximum=max(Sample), count = n())
```

###Model
- **Model day 8 WEIGHT**
```{r,}
mod1<-lm(Sample ~ Tx + CCTB + Group, data=Day8)
summary(mod1)
```

-Confidence intervals
```{r, echo=FALSE}
confint(mod1)
```

- Diferences between treatment groups
```{r, echo=FALSE}
mul <- glht(mod1, linfct = mcp(Tx = "Tukey")) # replace Tukey with Dunnett
summary(mul)
```

- **Model day 16 WEIGHT**
```{r}
mod2<-lm(Sample ~ Tx + CCTB + Group, data=Day16)
summary(mod2)
```

- Confidence Intervals
```{r, echo=FALSE}
confint(mod2)
```

- Difrences between treatment groups
```{r, echo=FALSE}
mul <- glht(mod2, linfct = mcp(Tx = "Tukey")) # replace Tukey with Dunnett
summary(mul)
```

###Models assumption check

- Day 8
```{r, echo=FALSE}
par(mfrow=c(2,2))
plot(mod1)
```

- Day 16
```{r, echo=FALSE}
par(mfrow=c(2,2))
plot(mod2)
```

###Plots
```{r, echo=FALSE}
D_M %>%
  ggplot(aes(x= factor(Tx, level = c("dext","hpms")) , y= Sample, group=Tx))+
  geom_boxplot(size=1) +
  theme_bw() +
  theme(text = element_text(color = "black"),
        plot.title=element_text(size=20, vjust = - 11, hjust = 0.07, face= "bold"),
        plot.subtitle=element_text(size=12),
        axis.title= element_text(size=16),
        axis.text.x = element_text(size = 16, face="bold", colour = "black"),
        axis.text.y = element_text(size = 16), 
        strip.background = element_rect(fill="grey"),
        strip.text = element_text(size = 18),
        axis.title.x = element_blank(), # remove x axis title
        panel.grid.major.x = element_blank() # remove vertical lines
        )+
  labs(title="Riboflavin Carrier",
       x=expression("Treatment group"),
       y=expression("Weight"~(mu*g)))+
  scale_x_discrete (labels=c("Control","Dextran","HMPC")) + 
  facet_grid (DW~., scales="free_y")
```


##Riboflavin replenishment

```{r, include=FALSE}
Rep <- Dat %>%
  filter(Ex == "Rep")

Day8 <- subset(Rep, DW == 8)
Day16 <- subset(Rep, DW== 16)
```

*Is there a difference in CCTB between treatment groups*

- day 16 only to control group
```{r, echo=FALSE}
TukeyHSD(aov(data = Day8, CCTB~Tx))
TukeyHSD(aov(data = Day16, CCTB~Tx))
```

###Weight

- Weight of samples day 8
```{r, echo=FALSE}
Day8 %>%
  group_by(Tx) %>%
  summarize(Mean=mean(Sample),sdSample=sd(Sample), Minimum=min(Sample), Maximum=max(Sample), count = n())
```

- Weight of samples day 16
```{r, echo=FALSE}
Day16 %>%
  group_by(Tx) %>%
  summarize(Mean=mean(Sample),sdSample=sd(Sample), Minimum=min(Sample), Maximum=max(Sample), count = n())
```

###Model

- **Model day 8 WEIGHT**
```{r,}
mod1<-lm(Sample ~ Tx + CCTB, data=Day8)
summary(mod1)
```

- Confidence intervals
```{r, echo=FALSE}
confint(mod1)
```

- Diferences between treatment groups
```{r, echo=FALSE}
mul <- glht(mod1, linfct = mcp(Tx = "Tukey")) # replace Tukey with Dunnett
summary(mul)
```

- **Model day 16 WEIGHT**
```{r}
mod2<-lm(Sample ~ Tx + CCTB, data=Day16)
summary(mod2)
```

- Confidence Intervals
```{r, echo=FALSE}
confint(mod2)
```

- Difrences between treatment groups
```{r, echo=FALSE}
mul <- glht(mod2, linfct = mcp(Tx = "Tukey")) # replace Tukey with Dunnett
summary(mul)
```

###Models assumption check

- Day 8
```{r, echo=FALSE}
par(mfrow=c(2,2))
plot(mod1)
```

- Day 16
```{r, echo=FALSE}
par(mfrow=c(2,2))
plot(mod2)
```

```{r, include=FALSE}
levels(Rep$DW)[levels(Rep$DW)=="8"] <- "Day 8"
levels(Rep$DW)[levels(Rep$DW)=="16"] <- "Day 16"
```

###Plots
```{r, echo=FALSE}
Rep %>%
  ggplot(aes(x= factor(Tx, level = c("0","yes_r","no_r")) , y= Sample, group=Tx))+
  geom_boxplot(size=1) +
  theme_bw() +
  theme(text = element_text(color = "black"),
        plot.title=element_text(size=20, vjust = - 11, hjust = 0.07, face= "bold"),
        plot.subtitle=element_text(size=12),
        axis.title= element_text(size=16),
        axis.text.x = element_text(size = 16, face="bold", colour = "black"),
        axis.text.y = element_text(size = 16), 
        strip.background = element_rect(fill="grey"),
        strip.text = element_text(size = 18),
        axis.title.x = element_blank(), # remove x axis title
        panel.grid.major.x = element_blank() # remove vertical lines
        )+
  labs(title="Replenishmet",
       x=expression("Treatment group"),
       y=expression("Weight"~(mu*g)))+
  scale_x_discrete (labels=c("Control","Yes","No")) + 
  facet_grid (DW~., scales="free_y")
```


#Temperature

```{r, include=FALSE}
Temp <- read_excel("C:\\Users\\yoga\\OneDrive - Universit채t Z체rich UZH\\backup\\Work\\Lab_UZH\\PepsinDigestion\\New\\Data\\Temp.xlsx")
```

```{r, include=FALSE}
Temp$Dose<-as.factor(Temp$Dose)
Temp$Eye<-as.factor(Temp$Eye)
```

```{r, echo=FALSE}
Temp1<-subset(Temp, Analysis==1)

t1<-Temp1 %>%
  ggplot(aes(x=Dose, y=Temp, color= Eye, group=Eye))+
  geom_point(size=2)+
  geom_line(size=0.7)+
  scale_color_manual(values=c("#a6611a", "#dfc27d", "#80cdc1",
                              "#018571", "#000000"))+
  theme_bw()+
  theme(legend.position = "bottom")+
  theme(plot.title = element_text(size = 10, face = "bold"),
        legend.title=element_text(size=10), 
        legend.text=element_text(size=10), 
        panel.grid.major.x = element_blank(),# remove vertical lines
        panel.grid.minor = element_blank(),
        legend.key.size = unit(1.5, "cm"), #change legend size
        legend.key.width = unit(3,"cm")
        )
t1
```
